$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Added extra detail about superpotential bilinear term
Changed wording in comment slightly

The full superpotential for $E_6$ inspired models will then be,
\be
W_{E_6} = W_0 + W_1 + W_2 , \label{Eq:e6-superpot}
\ee
where
\begin{eqnarray}
W_0 &=& \lambda_{ijk} \hat{S}_i \hat{H}^d_{j} \cdot\hat{H}^u_{k} +
\kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\overline{D}}_k + h^N_{ijk} \hat{N}^c_i
\hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
& & + y^U_{ijk} \hat{u}^c_i \hat{H}^u_{j} \cdot \hat{Q}_k + y^D_{ijk}
\hat{d}^c_i \hat{Q}_k \cdot \hat{H}^d_{j} + y^E_{ijk} \hat{e}^c_i \hat{L}_k
\cdot\hat{H}^d_{j} , \\
W_1 &=& g^Q_{ijk} \hat{D}_i \hat{Q}_j \cdot \hat{Q}_k + g^q_{ijk}
\hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k , \\
W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i
\hat{D}_j \hat{u}^c_k + g^D_{ijk} \hat{Q}_i \cdot \hat{L}_j \hat{\bar{D}}_k .
\label{Eq:e6-superpot-parts}
\end{eqnarray}
Nonetheless while this model is very elegant so far, the
superpotential of Eq.~(\ref{Eq:e6-superpot}) contains dangerous terms which
can induce proton decay and lead to large flavour changing neutral
currents (FCNCs).  There are a number of approaches to suppress these
terms, involving the use of different discrete symmetries.  Here for
the purposes of renormalization group running we will simply include
the following unsuppressed superpotential terms, which follows the
approach taken in work on the cE$_6$SSM \cite{Athron:2009ue, Athron:2009bs},
%
%% \begin{align}
%%   \begin{split}
    \ba
    W &\approx& y_{\tau} \SuperField{L}_3 \cdot \SuperField{H}_d
      \SuperField{e}^c_3 + y_b \SuperField{Q}_3\cdot\SuperField{H}_d
      \SuperField{d}_3^c + y_t \SuperField{H}_u\cdot\SuperField{Q}_3
      \SuperField{u}_3^c\nonumber\\
    &&
    + \lambda_i \SuperField{S} \SuperField{H}_i^d
    \cdot \SuperField{H}_i^u  + \kappa_i \SuperField{S} \SuperField{D}_i
    \SuperField{\overline{D}}_i + \mu' \SuperField{H}'\cdot
    \SuperField{\overline{H'}},
    \ea
  %% \end{split}
  \label{SuPot_RGE}
%%\end{align}
%
where we denote by $\SuperField{H}_d^3 \equiv \SuperField{H}_d$,
$\SuperField{H}_u^3 \equiv \SuperField{H}_u$ and $\SuperField{S}_3 \equiv
\SuperField{S}$ the third generation Higgs and SM singlet fields that are
assumed to acquire non-zero VEVs.  In addition to the $E_6$ preserving terms
following from Eq.~(\ref{Eq:e6-superpot}), this superpotential also contains a
single $E_6$ violating bilinear term $\mu' \SuperField{H}'\cdot
\SuperField{\overline{H'}}$.  This term is responsible for setting the masses of
the components of the superfields $\SuperField{H}'$,
$\SuperField{\overline{H'}}$, but it is not involved in the process of EWSB.
Consequently the impact on the fine tuning of the value of $\mu'$ is much
smaller than that coming from other sectors, and so can be safely neglected in
our study. In all of the scans we present below the value of $\mu'$ is fixed
to $\mu' = 5$ TeV.

>>>>

The full superpotential for $E_6$ inspired models will then be,
\be
W_{E_6} = W_0 + W_1 + W_2 , \label{Eq:e6-superpot}
\ee
where
\begin{eqnarray}
W_0 &=& \lambda_{ijk} \hat{S}_i \hat{H}^d_{j} \cdot\hat{H}^u_{k} +
\kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\overline{D}}_k + h^N_{ijk} \hat{N}^c_i
\hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
& & + y^U_{ijk} \hat{u}^c_i \hat{H}^u_{j} \cdot \hat{Q}_k + y^D_{ijk}
\hat{d}^c_i \hat{Q}_k \cdot \hat{H}^d_{j} + y^E_{ijk} \hat{e}^c_i \hat{L}_k
\cdot\hat{H}^d_{j} , \\
W_1 &=& g^Q_{ijk} \hat{D}_i \hat{Q}_j \cdot \hat{Q}_k + g^q_{ijk}
\hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k , \\
W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i
\hat{D}_j \hat{u}^c_k + g^D_{ijk} \hat{Q}_i \cdot \hat{L}_j \hat{\bar{D}}_k .
\label{Eq:e6-superpot-parts}
\end{eqnarray}
Nonetheless while this model is very elegant so far, the
superpotential of Eq.~(\ref{Eq:e6-superpot}) contains dangerous terms which
can induce proton decay and lead to large flavour changing neutral
currents (FCNCs).  There are a number of approaches to suppress these
terms, involving the use of different discrete symmetries.  Here for
the purposes of renormalization group running we will simply include
the following unsuppressed superpotential terms, which follows the
approach taken in work on the cE$_6$SSM \cite{Athron:2009ue, Athron:2009bs},
%
%% \begin{align}
%%   \begin{split}
    \ba
    W &\approx& y_{\tau} \SuperField{L}_3 \cdot \SuperField{H}_d
      \SuperField{e}^c_3 + y_b \SuperField{Q}_3\cdot\SuperField{H}_d
      \SuperField{d}_3^c + y_t \SuperField{H}_u\cdot\SuperField{Q}_3
      \SuperField{u}_3^c\nonumber\\
    &&
    + \lambda_i \SuperField{S} \SuperField{H}_i^d
    \cdot \SuperField{H}_i^u  + \kappa_i \SuperField{S} \SuperField{D}_i
    \SuperField{\overline{D}}_i + \mu' \SuperField{H}'\cdot
    \SuperField{\overline{H'}},
    \ea
  %% \end{split}
  \label{SuPot_RGE}
%%\end{align}
%
where we denote by $\SuperField{H}_d^3 \equiv \SuperField{H}_d$,
$\SuperField{H}_u^3 \equiv \SuperField{H}_u$ and $\SuperField{S}_3 \equiv
\SuperField{S}$ the third generation Higgs and SM singlet fields that are
assumed to acquire non-zero VEVs.  In addition to the $E_6$ preserving terms
following from Eq.~(\ref{Eq:e6-superpot}), this superpotential also contains a
bilinear term $\mu' \SuperField{H}'\cdot \SuperField{\overline{H'}}$ that
violates the $E_6$ symmetry but is invariant with respect to the low energy SM
gauge group and the additional $U(1)'$ symmetry.  This term is responsible for
setting the masses of the components of the superfields $\SuperField{H}'$,
$\SuperField{\overline{H'}}$, but it is not involved in the process of EWSB.
Consequently the impact on the fine tuning of the value of $\mu'$ is much
smaller than that coming from other sectors, and so can be safely neglected
in our study. In all of the scans we present below the value of $\mu'$ is
fixed to $\mu' = 5$ TeV.
